---
title: "Dialogue Data Evaluation"
author: "Zoltán Csik"
date: "2023-09-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Evaluation

This R Markdown serves the purpose of evaluating acquired dialogue data. The collected data represents several linguistic dialogue features.
Goal of this analysis:
  - Determine the mean value for each linguistic feature that was measured. 

```{r, include=FALSE}
# Creating the Data Frame
dialogue_data <- data.frame(
  Feature = c("Sentence Length", 
              "Words per Sentence", 
              "Unique words per Sentence", 
              "Lexical Diversity"),
  HH1 = c(52.558, 13.767, 12.093, 9.287),
  HH2 = c(55.209, 13.478, 11.791, 11.006),
  HH3 = c(73.681, 20.931, 17.056, 9.816),
  HC1 = c(33.372, 8.721, 8.093, 9.618),
  HC2 = c(22.452, 5.71, 5.613, 6.915),
  HC3 = c(38.393, 9.714, 8.857, 8.277)
)
```
```{r, include=TRUE}
dialogue_data
```

# Divided Dialogues:
To compare human-human data with human-robot data, the dataframe has to be split into two:

```{r, include=FALSE}
# Splitting the dataframe

# Data Frame with HH1 to HH3
dialogue_HH <- dialogue_data[, c("Feature", "HH1", "HH2", "HH3")]

dialogue_HC <- dialogue_data[, c("Feature", "HC1", "HC2", "HC3")]
```

```{r, include=TRUE}
dialogue_HH
dialogue_HC
```
\newpage
# Human-Human Diaogue Data
Count the mean value for each linguistic feature data:
```{r, include=FALSE}
# Compute the mean for each measurement
dialogue_HH$Mean <- rowMeans(dialogue_HH[, 2:4])
```
```{r, include=TRUE}
dialogue_HH
```

