---
title: "Dialogue Data Evaluation"
author: "Zoltán Csik"
date: "2023-09-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

# Data Preparation

This R Markdown serves the purpose of evaluating acquired dialogue data. The collected data represents several linguistic dialogue features.

```{r, include=FALSE}
# Creating the Data Frame
dialogue_data <- data.frame(
  Feature = c("Sentence Length", 
              "Words per Sentence", 
              "Unique words per Sentence", 
              "Lexical Diversity"),
  HH1 = c(52.558, 13.767, 12.093, 9.287),
  HH2 = c(55.209, 13.478, 11.791, 11.006),
  HH3 = c(73.681, 20.931, 17.056, 9.816),
  HC1 = c(33.372, 8.721, 8.093, 9.618),
  HC2 = c(22.452, 5.71, 5.613, 6.915),
  HC3 = c(38.393, 9.714, 8.857, 8.277)
)
```

```{r, include=TRUE, echo=FALSE}
dialogue_data
```

# Divided Dialogues:

To compare human-human data with human-robot data, the dataframe has to be split into two:

```{r, include=FALSE}
# Splitting the dataframe

# Data Frame with HH1 to HH3
dialogue_HH <- dialogue_data[, c("Feature", "HH1", "HH2", "HH3")]

dialogue_HC <- dialogue_data[, c("Feature", "HC1", "HC2", "HC3")]
```

```{r, include=TRUE, echo=FALSE}
dialogue_HH
dialogue_HC
```

# Human-Human Diaogue Data

Count the mean value for each linguistic feature data:

```{r, include=FALSE}
# Compute the mean for each measurement
dialogue_HH$Mean <- rowMeans(dialogue_HH[, 2:4])
```

```{r, include=TRUE, echo=FALSE}
dialogue_HH
```

\newpage

# Human-Robot Diaogue Data

Count the mean value for each linguistic feature data:

```{r, include=FALSE}
# Compute the mean for each measurement
dialogue_HC$Mean <- rowMeans(dialogue_HC[, 2:4])
```

```{r, include=TRUE, echo=FALSE}
dialogue_HC
```

# Combined Mean Values

Combine mean values from both Data Frames

```{r, include=FALSE}
  dialogue_summary <- data.frame(
  Feature = dialogue_HH$Feature,
  HH = dialogue_HH$Mean,
  HC = dialogue_HC$Mean
)
```

# Visual Comparison

```{r, include=TRUE, echo=FALSE}
  ggplot(dialogue_summary) + 
  geom_bar(aes(x = Feature, y = HH, fill = "Human-Human"), stat = "identity", position = "dodge") + 
  geom_bar(aes(x = Feature, y = HC, fill = "Human-Computer"), stat = "identity", position = "dodge") +
  scale_fill_manual(values=c("Human-Human"="darkgreen", "Human-Computer"="lightgreen")) +
  scale_y_continuous(breaks = seq(0, max(dialogue_summary$HH, na.rm = TRUE), by = 2)) +
  theme_minimal() +
  labs(title = "Comparison of HH and HC", y = "Mean Measurement", x = "Linguistic Dialogue Feature", fill = "Type of Dialogue") +
  theme(axis.text.x = element_text(size = 6, hjust = 1, angle = 45),
        plot.title.position = "plot",
        axis.text.y = element_text(size = 4),
        plot.title = element_text(hjust = 0.5),
        plot.margin = margin(1.1, 1.1, 1.1, 1.1, "cm"))
```

\newpage

# Statistical Relevance
Since we have two different types of Dialogues, the Two-sample independent t-test is applied:

### First application: sentence lengths compared
```{r, include=TRUE, echo=FALSE}
# Test 1 - Sentence length
group_1_sentence <- c(dialogue_HH$HH1[1], dialogue_HH$HH2[1], dialogue_HH$HH3[1])
group_2_sentence <- c(dialogue_HC$HC1[1], dialogue_HC$HC2[1], dialogue_HC$HC3[1])
t.test(group_1_sentence, group_2_sentence)
```
### Second application: Average words compared
```{r, include=TRUE, echo=FALSE}
# Test 2 - Average word count
group_1_word <- c(dialogue_HH$HH1[2], dialogue_HH$HH2[2], dialogue_HH$HH3[2])
group_2_word <- c(dialogue_HC$HC1[2], dialogue_HC$HC2[2], dialogue_HC$HC3[2])
t.test(group_1_word, group_2_word)
```

### Third application: Average unique words compared
```{r, include=TRUE, echo=FALSE}
# Test 2 - Average unique word count
group_1_unique_word <- c(dialogue_HH$HH1[3], dialogue_HH$HH2[3], dialogue_HH$HH3[3])
group_2_unique_word <- c(dialogue_HC$HC1[3], dialogue_HC$HC2[3], dialogue_HC$HC3[3])
t.test(group_1_unique_word, group_2_unique_word)
```

### Fourth application: Lexical Diversity
```{r, include=TRUE, echo=FALSE}
# Test 2 - Average unique word count
group_1_lex <- c(dialogue_HH$HH1[4], dialogue_HH$HH2[4], dialogue_HH$HH3[4])
group_2_lex <- c(dialogue_HC$HC1[4], dialogue_HC$HC2[4], dialogue_HC$HC3[4])
t.test(group_1_lex, group_2_lex)
```